Tidal Locking in Low-Mass Stellar Binary Stars

### 2018-11-02 Paper/sync.tex
Updates from ShareLaTeX

Abstract

@@

 Equilibrium tidal models, first introduced by \citep{Darwin1880}, track the secular evolution of an orbiter's semi-major axis, $a$, eccentricity, $e$, and the rotation rates, $\omega$, and obliquities $\psi$, of the both gravitating bodies due to tidal torques. Equilibrium tidal models assume that tidally-interacting bodies raise tidal bulges on their companions that remain offset from the line connecting the both bodies' centers of mass due to friction within each body.  The tidal bulges cause torques that drive the exchange of angular momentum between the orbit and both bodies' spins. Equilibrium tidal models are linear since they assume that the tidal waves that comprise the tidal bulge raised on a body are uncoupled. Under these assumptions, the tidal evolution is analogous to a driven, damped harmonic oscillator \citep{Greenberg2009}.  We refer the reader to \citet{Barnes2017} for an in-depth discussion of the assumptions and limitations of equilibrium tidal models.  Although simple, equilibrium tidal models have been used to robustly model the secular orbital and rotation evolution of both Solar System bodies and exoplanets \citet[e.g.][]{Goldreich1966,Jackson2009,Leconte2010,Heller2011,Barnes2013,Barnes2017} and stellar binaries \citep[e.g.][]{Zahn1989,Zahn2008,Repetto2014,Fleming2018}.  Here, we consider two equilibrium tidal models to study the secular spin-orbital evolution of low-mass stellar binaries.

@@

>>>>

-tidally locking before 5 Gyr occurs for most binaries below orbital periods of 60-70 days regardless of tidal parameter

-compute cumulative fraction of tidal-locking times in Porb bins plot so I can say x fraction are stars with Porb $< 60$d are tidally locked.

-make locking.py plot from previous paper with new data

- 5 points with Porb < 10 days and Porb/Prot > 10 in lurie plot are likely young stars that have or continue to spin up via angular momentum conservation due to pre main sequence contraction.  evidence for young stars in the Kepler field, e.g. McQuillan+2014, Matt+2015, Davenport+2017,2018 support this theory

- Lurie has some binaries with Porb/Prot = 0.9, subsynchronous rotators.  cite his explaination for them

- Lurie finds tons of short Porb EBs because transit observational biases favor bodies with short orbital periods for a finite observing window, eg Kepler's lifetime

@@

 Equilibrium tidal models, first introduced by \citep{Darwin1880}, track the secular evolution of an orbiter's semi-major axis, $a$, eccentricity, $e$, and the rotation rates, $\omega$, and obliquities $\psi$, of the both gravitating bodies due to tidal torques. Equilibrium tidal models assume that tidally-interacting bodies raise tidal bulges on their companions that remain offset from the line connecting the both bodies' centers of mass due to friction within each body.  The tidal bulges cause torques that drive the exchange of angular momentum between the orbit and both bodies' spins. Equilibrium tidal models are linear since they assume that the tidal waves that comprise the tidal bulge raised on a body are uncoupled. Under these assumptions, the tidal evolution is analogous to a driven, damped harmonic oscillator \citep{Greenberg2009}.  We refer the reader to \citet{Barnes2017} for an in-depth discussion of the assumptions and limitations of equilibrium tidal models.  Although simple, equilibrium tidal models have been used to robustly model the secular orbital and rotation evolution of both Solar System bodies and exoplanets \citet[e.g.][]{Goldreich1966,Jackson2009,Leconte2010,Heller2011,Barnes2013,Barnes2017} and stellar binaries \citep[e.g.][]{Zahn1989,Zahn2008,Khaliullin2011,Repetto2014,Fleming2018}.  Here, we consider two equilibrium tidal models to study the secular spin-orbital evolution of low-mass stellar binaries.

@@

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{../Plots/lockTimePorbHist.pdf}
   \caption{Caption.}%
    \label{fig:lockHistPorb}%
\end{figure}
